A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise ITE operator

Accoring to Brace et al.~\cite{BRACE90}, the $ITE$ operator forms the core of an
efficient OBDD package implementation. Hence, they used a hash-based cache, called
\textit{caching computed-table}, to implement it, exploiting a high locality of
reference and consuming less memory.

Compared to using a normal hash table, this results in more recursive calls to 
$ITE$ (because of cache misses) but less time spent in garbage collection
(described in Section~\ref{subsec:garbage-collection}) and look-ups (because no
collision chains need to be searched).

@@

Brace et al.~\cite[p. 42]{BRACE90} provides the pseudocode of the $ITE$ algorithm
as well as a modification, called $ite\_constant$, which can be used to implement
logical implication tests more efficiently by avoiding the construction of
intermediate nodes. \tbr

>>>>

Accoring to Brace et al.~\cite{BRACE90}, the $ITE$ operator forms the core of an
efficient OBDD package implementation. Hence, they used a hash-based cache, called
\textit{caching computed-table}, to implement it, exploiting a high locality of
reference and thus consuming less memory.

Compared to using a normal hash table, this results in more recursive calls 
(because of cache misses) but less time spent in garbage collection (described
in Section~\ref{subsec:garbage-collection}) and look-ups (because no collision
chains need to be searched).

@@

Brace et al.~\cite[p. 42]{BRACE90} provides the pseudocode of the $ITE$ algorithm
as well as a modification, called $ite\_constant$, which can be used to implement
logical implication tests more efficiently by avoiding the construction of
intermediate nodes.
